Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-05-23 vesicle_code/docs/adhesion/adhesion.tex
fixing up intrinsic viscosity images
fixed up text in intrinsic viscosity calculation

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, and $\xxi$ is
the traction as defined in equation~\eqref{eqn:traction}.  In the left
plot of Figure~\ref{fig:shearIntrinsicViscosity}, we compare the
intrinsic viscosity of a single tank-treading vesicle to a doublet.  To
validate our simulations, we superimpose (black marks) the intrinsic
viscosity calculated by Ghigliotti {\em et
al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
significantly increases the intrinsic viscosity at all the reduced
areas.  To further characterize the effect of adhesion, in the right
plot of Figure~\ref{fig:shearIntrinsicViscosity} we decompose the
intrinsic viscosity into the contributions from the bending and tension
(blue), and the contribution from the adhesion (red).  We also
superimpose twice the intrinsic viscosity of a single tank-treading
vesicle (dashed curve) to demonstrate that the bending and tension of
the doublet behave similarly, but not identically, to a dilute
suspensions of non-adhering tank-treading vesicles.  We see that the
effect of the adhesion on the intrinsic viscosity is largest for
vesicles with small reduced areas.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
  0.7$, and the separation distance is $\delta = 0.4$.  The black marks
  denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
  Right}: The decomposition of the intrinsic viscosity into the
  contributions for the bending and tension (blue) of the vesicles, and
  the contribution from the vesicle adhesion (red).  Also included is
  twice the intrinsic viscosity of a single tank-treading vesicle
  (dashed black line).}
\end{figure}

>>>>

Finally, we investigate the rheology of a suspension of a doublet by
computing the effective viscosity of a doublet and compare it to the
effective viscosity of a single tank-treading vesicle. The effective
viscosity is defined as the viscosity of a homogeneous Newtonian fluid
with the same energy dissipation per macroscopic element of fluid.  In a
simple shear flow, the intrinsic viscosity, $[\mu]$ is
\begin{align*}
  [\mu]:= \frac{\mu_{\mathrm{eff}} - \mu_0}{\phi \mu_0} = 
  \frac{1}{\chi \mu_0 (T_e - T_i)} \int_{T_i}^{T_e} 
  \langle \tau_{12} \rangle dt,
\end{align*}
where
\begin{align*}
  \langle \tau \rangle = \frac{1}{|\omega|} \int_{\gamma}
    \xxi \otimes \xx ds,
\end{align*}
$\phi$ is the area fraction of vesicles, $\tau$ is the stress due to the
vesicles, $\langle \cdot \rangle$ is the spatial average, $|\omega|$ is
the total area of both vesicles, and $\xxi$ is the traction as defined
in equation~\eqref{eqn:traction}.  In the left plot of
Figure~\ref{fig:shearIntrinsicViscosity}, we compare the intrinsic
viscosity of a single tank-treading vesicle to a doublet.  To validate
our simulations, we superimpose (black marks) the intrinsic viscosity
calculated by Ghigliotti {\em et
al.}~\cite{GhigliottiBibenMisbah2010_JFM}.  The presence of the doublet
slightly increases the intrinsic viscosity at all the reduced
areas.  To further characterize the effect of adhesion, in the right
plot of Figure~\ref{fig:shearIntrinsicViscosity} we decompose the
intrinsic viscosity into the contributions from the bending and tension
(blue), and the contribution from the adhesion (red).  We also
superimpose the intrinsic viscosity of a single tank-treading
vesicle (dashed curve) to demonstrate that the bending and tension of
the doublet behave similarly, but not identically, to a dilute
suspensions of non-adhering tank-treading vesicles.  We see that the
effect of the adhesion on the intrinsic viscosity is largest for
vesicles with small reduced areas.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/shear2Ves_adR4em1adS7em1Chi5em1.pdf}
  \includegraphics[width=0.45\textwidth]{figs/doublet_decomp.pdf}
  \caption{\label{fig:shearIntrinsicViscosity} {\em Left}: The intrinsic
  viscosity of a tank-treading vesicle (blue) and a doublet (red).  The
  shear rate is $\chi = 0.5$, the Hamaker constant is $\mathcal{H} =
  0.7$, and the separation distance is $\delta = 0.4$.  The black marks
  denote intrinsic viscosity values computed by Ghigliotti {\em et
  al.}~\cite{GhigliottiBibenMisbah2010_JFM} (cf.~Figure 5).  {\em
  Right}: The decomposition of the intrinsic viscosity into the
  contributions for the bending and tension (blue) of the vesicles, and
  the contribution from the vesicle adhesion (red).  Also included is
  the intrinsic viscosity of a single tank-treading vesicle (dashed
  black line).}
\end{figure}
